\Large{Peer Review} \\ \huge\textbf{{A Modern Look at Introductory Programming Languages}}

### 2018-05-08 peer-reveiw/review_one.tex
finished question 4
finished question 5

\documentclass{article}
    \usepackage[utf8]{inputenc}

@@

    \section*{}
    \textbf{3. } At the moment, no evaluation has been provided. Although, I believe it is a little early to ask this question.
    \end{document}

>>>>

\documentclass{article}
    \usepackage[utf8]{inputenc}
    \usepackage[a4paper,left=1.5cm,right=1.5cm,top=4cm,bottom=4cm]{geometry}

@@

    \section*{}
    \textbf{3. } At the moment, no evaluation has been provided. Although, I believe it is a little early to ask this question.

    \section*{}
    \textbf{4 .} Layout and formatting is acceptable by me. I like that the paper is constructed as a two-column paper. In my opinion, it makes it easier for the reader to follow the material.

    \section*{}
    \textbf{5 .} The English language being used is good enough. Nonetheless, I had one suggestion on the writing style. In the introduction of the \textit{Criteria} section, the word criteria is being used 6 times in just 7 sentences. I doesn't sound nice to hear in your head while reading one word repeated so often. Thus, I would recommend avoiding repetitions. In seven sentences, the word criteria could be used at most 2 times. In order to achieve this, synonyms could be used or sentences could be constructed in such a way that the usage of the word would be minimized.    
    \end{document}
